\bf Hierarchical Forecasts Reconciliation

### 2019-07-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added discussion of generalised Euclidean disatance

>>>>

	In particular, this measure is the

	One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of {\em all} variables in the hierarchy.  A clear shortcoming of this measure of forecast accuracy is that forecasts errors in all series should not necessarily be treated equally.  For example, in hierarchies, top-level series tend to have a much larger scale than bottom level series.  Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating square errors.  An even more sophisticated understanding may take the correlation between series into account.  All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.  Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.

	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix.  However this matrix can be considered to be an orthogonal projection for a different geometry, namely the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.  One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.  This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.  The transformed reconciled forecast results from an orthogonal projection in the transformed space since

	\begin{align}
	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}
	\end{align}

	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{1}\bm{v}$.  This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.  In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.  For diagonal $\bm{W}$ this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix this is equivalent to a Mahalanobis distance.  As such Theorem~\ref{th:distred} can easily be generalised.  If the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
